### 2023-05-22 resilience-safe-up.tex
up
downward closed and upward closed are now consistently written with a '-'

%
%		cas étudié par les deux articles sur les graphes
%
Let us choose $\Bad$ to be the set of states from which there is no infinite run. If we are in an upward compatible ordered transition system (like VASS, lossy channel systems,...), then $\Bad$ is downward closed.

@@

example: in a VASS, we may choose $\Safe$ to be the set of states that are not deadlocks, i.e. from which it is always possible to fire a transition. This set of states is upward closed and $\Safe=S-\Bad=\uparrow \Safe$.

>>>>

%
%		cas étudié par les deux articles sur les graphes
%
Let us choose $\Bad$ to be the set of states from which there is no infinite run. If we are in an upward compatible ordered transition system (like VASS, lossy channel systems,...), then $\Bad$ is downward-closed.

@@

example: in a VASS, we may choose $\Safe$ to be the set of states that are not deadlocks, i.e. from which it is always possible to fire a transition. This set of states is upward-closed and $\Safe=S-\Bad=\uparrow \Safe$.

### 2023-05-22 resilience.tex
downward closed and upward closed are now consistently written with a '-'

% \mathieu{En fait de plus en plus j'ai l'impression que on peut se passer des neutres: même dans une situation où on aurait des configurations neutre j'aurais tendance à dire qu'on peut se ramener à un cas safe complémentaire de bad en duplicants les neutres en deux parties, une avec "on a vu un very bad récement il faut aller vers safe" (et qui dans le nouveau modèle seraient donc bad) et une "on a pas vu de very bad tout vas bien" (et qui dans le nouveau modèle seraient donc safe)
% $=>$ Rédiger ça plus proprement}
While considering a sequence of configurations, every prefix is always 
either in the case that the latest visited $\Bad$ configuration has already been followed by a $\Safe$ configuration
or in the case that it still has to. 
Thus, in context, there are no true ``neutral'' configurations: either a neutral configuration is contextually ``$\Safe$'' because it follows a visit in a $\Safe$ configuration, either it is contextually ``$\Bad$'' because it follows a visit in a $\Bad$ configuration and has, accordingly, to reach a $\Safe$ one.
Hence we will consider not only $\Bad$ and $\Safe$ disjoint but
% w.l.o.g.
	also
$\Bad$ complement of $\Safe$,
in which case
if $\Bad$ is downward-closed then $\Safe$ is upward-closed and vice-versa.
Cases where $\Bad$ or $\Safe$ are not complements of each other, and share closure properties, i.e. they are both downward
closed or both upward-closed,
have also been studied, 
see 
Appendix~\ref{case down down}
and
Appendix~\ref{case up up} for results.

>>>>

% \mathieu{En fait de plus en plus j'ai l'impression que on peut se passer des neutres: même dans une situation où on aurait des configurations neutre j'aurais tendance à dire qu'on peut se ramener à un cas safe complémentaire de bad en duplicants les neutres en deux parties, une avec "on a vu un very bad récement il faut aller vers safe" (et qui dans le nouveau modèle seraient donc bad) et une "on a pas vu de very bad tout vas bien" (et qui dans le nouveau modèle seraient donc safe)
% $=>$ Rédiger ça plus proprement}
While considering a sequence of configurations, every prefix is always 
either in the case that the latest visited $\Bad$ configuration has already been followed by a $\Safe$ configuration
or in the case that it still has to. 
Thus, in context, there are no true ``neutral'' configurations: either a neutral configuration is contextually ``$\Safe$'' because it follows a visit in a $\Safe$ configuration, either it is contextually ``$\Bad$'' because it follows a visit in a $\Bad$ configuration and has, accordingly, to reach a $\Safe$ one.
Hence we will consider not only $\Bad$ and $\Safe$ disjoint but
% w.l.o.g.
	also
$\Bad$ complement of $\Safe$,
in which case
if $\Bad$ is downward-closed then $\Safe$ is upward-closed and vice-versa.
Cases where $\Bad$ or $\Safe$ are not complements of each other, and share closure properties, i.e. they are both downward-closed or both upward-closed,
have also been studied, 
see 
Appendix~\ref{case down down}
and
Appendix~\ref{case up up} for results.
